Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-04 paper.tex
trying to not mess things up

\subsection{Results}
In this specific study, one will only focus on the uncertainty on the produced
electric power as a function of time, on the total quantity of natural uranium
used and on the total unused fissile inventory (unused reprocessed plutonium).
In order to estimate the total uncertainty on those 3 parameters as well as the
individual contribution of the operational parameters several set of (199)
simulations have been completed.  All uncertainty are computed as the standard
deviation over over all the calculations in the set.

@@

\subsection{Conclusion}

>>>>

\section{Results}
In this specific study, one will only focus on the uncertainty on the produced
electric power as a function of time, on the total quantity of natural uranium
used and on the total unused fissile inventory (unused reprocessed plutonium).
In order to estimate the total uncertainty on those 3 parameters as well as the
individual contribution of the operational parameters several set of (199)
simulations have been completed.  All uncertainty are computed as the standard
deviation over over all the calculations in the set.

@@

\section{Conclusion}
